Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-15 src/article.tex
Revise discussion

  \paragraph*{Background:} Assembly of short-read sequencing data can result in
  a fragmented non-contiguous series of genomic sequences. Therefore a common
  step in a genome project is to join neighbouring sequence regions together
  and fill gaps \remove{in the assembly using additional sequences}. This
  scaffolding step, however, is non-trivial and requires manually editing large
  blocks of nucleotide sequence. Joining these sequences together also hides
  the source of each region in the final genome sequence. Taken together, these
  considerations may make reproducing or editing an existing genome build
  difficult.

@@

  \paragraph*{Results:} This software allows a genome \change{scaffold}{build}
  to be defined in terms of the constituent sequences using a relatively simple
  syntax\remove{to define the scaffold}. This syntax further allows unknown
  regions to be \change{defined}{specified} and add additional sequences to
  fill gaps in the scaffold. Defining the genome construction in a file makes
  the scaffolding process reproducible and easier to edit compared with
  \add{large} FASTA nucleotide sequences.

  \paragraph*{Conclusions:} Scaffolder is easy-to-use genome scaffolding
  software. This tool promotes reproducibility and continuous development in a
  genome project. Scaffolder can be found at \scaffolder.

>>>>

  \paragraph*{Background:} \add{The} assembly of \add{next-generation}
  short-read sequencing data can result in a fragmented non-contiguous series
  of genomic sequences. Therefore a common step in a genome project is to join
  neighbouring sequence regions together and fill gaps \remove{in the assembly
  using additional sequences}. This scaffolding step\remove{, however,} is
  non-trivial and requires manually editing large blocks of nucleotide
  sequence. Joining these sequences together also hides the source of each
  region in the final genome sequence. Taken together, these considerations
  may make reproducing or editing an existing genome \change{build}{scaffold}
  difficult.

@@

  \paragraph*{Results:} This software allows a genome \change{scaffold}{build}
  to be defined in terms of the constituent sequences using a relatively simple
  syntax\remove{to define the scaffold}. This syntax further allows unknown
  regions to be \change{defined}{specified} and add additional sequences to
  fill \add{known} gaps in the scaffold. Defining the genome construction in
  a file makes the scaffolding process reproducible and easier to edit
  compared with \add{large} FASTA nucleotide sequences.

  \paragraph*{Conclusions:} Scaffolder is easy-to-use genome scaffolding
  software\change{. This tool}{ which} promotes reproducibility and continuous
  development in a genome project. Scaffolder can be found at \scaffolder.
